---
title       : Mining the Movies of 2011
subtitle    : Top Movies from 2011
author      : Diane Reynolds
job         : Coursera - Johns Hopkins University - Data Products Course
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r, echo=FALSE, results='hide', warning=FALSE}
library(shiny)
library(dplyr)
library(UsingR)
library(ggplot2)

data(movie_data_2011)
movies <- filter(movie_data_2011, Genre != "")
movies <- movies %>% group_by(Movie) %>% 
  summarise(Genre=last(Genre), MaxGross=max(TotalGross))
movies <- movies[order(movies$MaxGross, decreasing=TRUE),]
buttons <- levels(movies$Genre)[levels(movies$Genre)!=""]
movies$Movie <- as.character(movies$Movie)
movies$Genre <- as.character(movies$Genre)

movie_count <- length(movies$Movie)
```
## Do you remember 2011?

We've developed an application to help you find great older movies to search for on Netflix or another streaming service.

2011 was a great year for movies, overall, `r movie_count` movies made the charts in 2011.

Load the app (URL available on the last slide) to select your favourite genre of movie and get a list of the top 10 movies in that genre from 2011.  Have more than one favourite?  Choose different genres as often as you like to get a new top 10 list!


--- .class #id

```{r, echo=FALSE, results='hide', warning=FALSE}
mygenre <- movies[movies$Genre=="Adventure",]
mygenre <- mygenre[1:10,]
mygenre$MaxGross <- mygenre$MaxGross/1000000
mygenre$Rank <- c(1:10)

advp <- ggplot(data=mygenre, aes(x=Rank, y=MaxGross, fill=Movie)) + 
  geom_bar(colour="black", fill="#DD8822", width=.8, stat="identity") + 
  guides(fill=FALSE) +
  xlab("Movie") + ylab("Total Gross Earnings (millions USD)") +
  ggtitle("Total Gross Earning for Top 10 Movies")
```

## Sample Top 10 List

```{r, echo=FALSE}
#advp
print("Top 10 Adventure Movies of 2011")
mygenre$Movie
```

--- .class #id

## 12 Genres to Choose Between!

Adventure movies not your thing?  That's okay - check out the plethora of great genres waiting for you to explore in the app!

```{r, echo=FALSE}
genres <- movies %>% group_by(Genre) %>%
  summarise(TotalEarnings=sum(MaxGross))

piec <- ggplot(genres, aes(x="", y=TotalEarnings, fill=Genre)) + 
  geom_bar(width = 1, stat = "identity") + 
  coord_polar("y", start=0)

piec
```

--- .class #id

## Links & Acknowledgements

### Links

1. You can find the application here:  https://dianereynolds.shinyapps.io/Movies2011/

2. The associated code, and these supporting slides are available on github here:  https://github.com/dianereynolds/MovieRankings2011.git

3. These slides are also available at Rpubs here: http://rpubs.com/Diane/greatmovies2011

### Acknowledgements

These slides and the associated app use a data set ("movie_data_2011") from the R package "UsingR" available on cran.


